EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-04 draft.tex
Update draft.tex

@@

@@

\subsection{Using the COCO Framework}
% BBOB Cases

The first step is to develop the search strategy
algorithms that are going to be used by the multi-population algorithm.
Algorithm developers can upload the container definition or images directly to
DockerHub; another option is to upload the container image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub; this
can be defined in DockerHub (or any other registry) too.  Docker Compose
configuration files can reference these images. When a user needs to deploy
the application, he or she needs to edit the {\tt docker-compose.yml} file
to specify the type and number of containers needed for the application.  The {\tt docker-compose}
application is responsible for starting all the containers, downloading new
versions if it is necessary. After starting the application, users can push
Experiment Definition files and start monitoring the execution in the terminal.
After the experiment is finished, the user must execute another script
that takes as argument the
experiment id to generate a collection of files containing all the
data generated by the experiment in a JSON format.
Researchers can use these files to analyze and plot experiment data.  Python
scripts are included in the repository to plot the running times for the
experiments, and all other plots used in this paper;  there is also a script to
generate the files needed by the COCO framework \cite{hansen2016coco}, which can generate standard
comparisons against other methods.

>>>>

Algorithm developers can upload the container definition or images directly to
DockerHub; another option is to upload the container image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub; this
can be defined in DockerHub (or any other registry) too.

@@

The administrator role is responsible for
editing the Docker Compose configuration files that reference the images created
by developers. To deploy the application, he or she needs to edit the {\tt
docker-compose.yml} file to specify the type and number of containers required
for the experiments. The {\tt docker-compose} application is responsible for
starting all the containers, and downloading new versions if it is necessary.

@@

After starting the application, users can push
Experiment Definition files and start monitoring the execution in the terminal.
After the experiment is finished, the user must execute another script
that takes as argument the experiment id to generate a collection of files containing all the
data generated by the experiment in a JSON format.

\subsection{Using the COCO Framework}

Researchers can use these files to analyze and plot experiment data.  Python
scripts are included in the repository to plot the running times for the
experiments, and all other plots used in this paper;  there is also a script to
generate the files needed by the COCO framework \cite{hansen2016coco}, which can generate standard
comparisons against other methods.
